Python as a machine learning language: experiences from the \sklearn project

### 2013-06-10 paper.tex
no need for nbsp before citations

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[authoryear]{natbib}
\usepackage{xcolor}
\usepackage{xspace}

@@

The \sklearn project~\citep{pedregosa2011} is an open source
machine learning library for the Python programming language. The ambition of
the project is to provide efficient and well-established machine learning tools
within a programming environment that is accessible to non-machine learning
experts and reusable in various scientific areas. In itself the project isn't
a novel domain-specific language, but a library that provides machine
learning idioms to a general-purpose high-level language. Among other things,
it includes classical learning algorithms, model selection tools and
preprocessing
procedures. From its core, the library has been designed to tie in with the set
of numeric and scientific packages centered around the Numpy and
SciPy~\citep{vanderwalt2011, varoquaux2013scipy} libraries.
As such, \sklearn is intended to be used within Python scripts
and requires some Python programming knowledge.
At the time, it offers no command line or graphical user interface.
% XXX Gael: maybe we should say that it augments a general purpose
% language with machine learning concepts, like numpy augments it with
% array-computing concepts.

@@

In \sklearn, we chose a representation of data that is as close as
possible to the matrix representation: datasets are encoded as NumPy
multidimensional arrays for dense data and as SciPy sparse matrices for sparse
data. While those may seem rather unsophisticated data representations when
compared to more object-oriented constructs, such as those used by
Weka~\citep{hall2009weka}, they bring the prime advantage of allowing us to rely
on all NumPy and SciPy vector operations -- often orders of magnitude faster
that the corresponding Python loops -- while allowing us at the same time to
keep the code short and readable.  This design choice has also been motivated by
the fact that, given their pervasiveness in many other scientific Python
packages, many scientific users of Python are already familiar with NumPy dense
arrays and SciPy sparse matrices, hence helping them to familiarize with the
project.  From a practical point of view, these formats also provide a bunch of
data loading and conversion tools which make them very easy to use in many
contexts. Moreover, for tasks where the inputs are text files or semi-structured
objects, we provide \textit{vectorizer} objects that efficiently convert such
data to the NumPy or SciPy formats.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{xcolor}
\usepackage{xspace}

@@

The \sklearn project \citep{pedregosa2011} is an open source
machine learning library for the Python programming language. The ambition of
the project is to provide efficient and well-established machine learning tools
within a programming environment that is accessible to non-machine learning
experts and reusable in various scientific areas. In itself the project isn't
a novel domain-specific language, but a library that provides machine
learning idioms to a general-purpose high-level language. Among other things,
it includes classical learning algorithms, model selection tools and
preprocessing
procedures. From its core, the library has been designed to tie in with the set
of numeric and scientific packages centered around the Numpy and
SciPy \citep{vanderwalt2011, varoquaux2013scipy} libraries.
As such, \sklearn is intended to be used within Python scripts
and requires some Python programming knowledge.
At present, it offers no command line or graphical user interface.
% XXX Gael: maybe we should say that it augments a general purpose
% language with machine learning concepts, like numpy augments it with
% array-computing concepts.

@@

In \sklearn, we chose a representation of data that is as close as
possible to the matrix representation: datasets are encoded as NumPy
multidimensional arrays for dense data and as SciPy sparse matrices for sparse
data. While those may seem rather unsophisticated data representations when
compared to more object-oriented constructs, such as those used by
Weka \citep{hall2009weka}, they bring the prime advantage of allowing us to rely
on all NumPy and SciPy vector operations -- often orders of magnitude faster
that the corresponding Python loops -- while allowing us at the same time to
keep the code short and readable.  This design choice has also been motivated by
the fact that, given their pervasiveness in many other scientific Python
packages, many scientific users of Python are already familiar with NumPy dense
arrays and SciPy sparse matrices, hence helping them to familiarize with the
project.  From a practical point of view, these formats also provide a bunch of
data loading and conversion tools which make them very easy to use in many
contexts. Moreover, for tasks where the inputs are text files or semi-structured
objects, we provide \textit{vectorizer} objects that efficiently convert such
data to the NumPy or SciPy formats.
